### 2017-09-30 icde/sec-exp.tex

In this section, we present an extensive experimental study of our approach \ensemblerank, compared with competitive methods.
Using three real-life scholarly datasets (\aan, \aminer and \magdata) and two sets of ground-truth (\recom and \fcita), we conducted four sets of experiments to evaluate: (1) the effectiveness of \ensemblerank,
%two sets of benchmark article pairs (\recom and \fcita) ranked by numbers of recommendations and future citations,
(2) the efficiency of our batch algorithm \batensemble and incremental algorithm \incensemble, and (3) the impacts of parameters. %\ie time decaying factor $\sigma$, importance weighting factor $\lambda$ and aggregating parameters $\alpha$ and $\beta$.

@@

We constructed two sets of ground-truth importance orders of article pairs, referred to as  \recom and \fcita.

@@

\noindent
(2) \fcita assumes that scholarly articles with more citations are of higher importance.
%
However, the number of entire citations is obviously biased to old articles. Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this only estimates future impacts of articles, not at the concerned time. For a fair ranking benchmark, we propose to use both past and future citations with the same period of time \wrt\ the concerned time, such that the number of citations within these two periods reveals the importance of articles at the concerned time.
%
We hence divided each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remaining part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
%
%
Moreover, articles in the same pairs were required to be in similar research fields, by utilizing the Fields-Of-Study information on \magdata~\cite{Sinha15:MAG}, and published in the same years, similar to~\cite{Wang16TIST}.
We used all pairs (around 50,000) for \aan, and randomly chose 300,000 pairs for both \aminer and \magdata.

@@

\stitle{Implementation}.
All algorithms were implemented with Microsoft Visual C++.
%Parameters.
For all algorithms, (a) the damping parameter $d$ and the iteration threshold $\epsilon$ were fixed to 0.85 and $10^{-8}$, respectively,
(b) the default splitting years were selected such that the part of data for ranking model accounted for around 75\% of the entire data, which were 2008 on \aan and 2012 on both \aminer and \magdata, and,
(c) for the sake of fairness, aggregating parameters of \futurerank, \hhgrank and \ensemblerank were tuned at the granularity of 0.1 and the best results were reported.
%
Moreover, $\rho$ was set to -0.2 for \futurerank following~\cite{sayyadi09}, and the time decaying factor $\sigma$ and the importance weighting factor $\lambda$ were set to -1 and 0.5  by default for \ensemblerank.

All experiments were conducted on a PC with 2 Intel Xeon E5--2630 2.4GHz CPUs and 64 GB of memory, running 64 bit Windows 7 professional system. The usage of virtual memory was forbidden. %in all of our tests.
When quantity measures are evaluated, the test was repeated over 5 times and the average results are reported.

@@

%\etitle{Remarks}.
In our tests we adopted a yearly update policy due the limitation of  available time information. In practice our algorithms may bring more efficiency benefits since the ranking is usually more frequent, such that the data updates are smaller and the unaffected area is very likely much larger.

@@

When varying $\alpha$ and $\beta$, the \PairAcc of \ensemblerank changes gently, as shown in Fig.~\ref{exp-ab}.
The optimal \PairAcc is obtained within a single region, rather than a complex collection of optimal regions.
%
Moreover, the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, as shown in Fig.~\ref{exp-ab}.
%For instance, consider a square of length 0.3, which covers 8.5\% of the parameter combination space. The fraction of parameters such that the \PairAcc is no worse than 1\% of the corresponding \PairAcc with marker $*$ is (73\%, 94\%) on \aan, (96\%, 87\%) on \aminer and (83\%, 95\%) on \magdata, using (\recom, \fcita), respectively.
%
Further, the optimal parameters on the same sets of ground-truth are very similar for (\aan, \aminer and \magdata), indicating that the setting of $\alpha$ and $\beta$ can be easily transferred across different datasets.
To conclude, \ensemblerank is very robust to parameters $\alpha$ and $\beta$, and it is quite flexible for choosing proper values of parameters $\alpha$ and $\beta$.

@@

When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than exploiting exponentially decayed weights directly without introducing the peak time.
The \PairAcc difference of these two algorithms is higher on \recom than on \fcita, since the two algorithms are just using citation information to predict past and future citations with \fcita.
Moreover, algorithm \ensemblerank is consistently better than \drank when $0.5 \le \lambda \le 0.9$.
%, which, with \recom and \fcita, improves the \PairAcc by (2.88\%, 3.91\%, 3.90\%) and (0.55\%, 0.50\%, 0.22\%) on (\aan, \aminer, \magdata) on average, respectively.
The improvement decreases with the decrease of $\lambda$ as the popularity dominates the ranking with small $\lambda$, and in some cases, \drank outperforms \ensemblerank. %as the prestige and popularity orders of article pairs are more diverse for \drank than \ensemblerank.
Overall, with \recom and \fcita, \ensemblerank improves the \PairAcc over \drank by (1.78\%, 3.07\%, 3.20\%) and (0.29\%, 0.48\%, 0.11\%) on (\aan, \aminer, \magdata) on average, respectively.

>>>>

In this section, we present an extensive experimental study of our approach \ensemblerank, compared with three competitive methods.
Using three real-life scholarly datasets (\aan, \aminer and \magdata) and two sets of ground-truth (\recom and \fcita), we conducted four sets of experiments to evaluate: (1) the effectiveness of \ensemblerank,
%two sets of benchmark article pairs (\recom and \fcita) ranked by numbers of recommendations and future citations,
(2) the efficiency of our batch algorithm \batensemble and incremental algorithm \incensemble, and (3) the impacts of parameters. %\ie time decaying factor $\sigma$, importance weighting factor $\lambda$ and aggregating parameters $\alpha$ and $\beta$.

@@

We constructed two sets of ground-truth importance ranking orders of article pairs, referred to as  \recom and \fcita.

@@

\noindent
(2) \fcita assumes that scholarly articles with more citations are of higher importance.
%
However, the number of entire citations is obviously biased to old articles. Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this only estimates future impacts of articles, not at the concerned time. For a fair ranking benchmark, we propose to use both past and future citations with the same period of time \wrt\ the concerned time, such that the number of citations within these two periods reveals the importance of articles at the concerned time.
%
We hence divide each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remaining part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
%
%
Moreover, articles in the same pairs were required to be in similar research fields, by utilizing the Fields-Of-Study information on \magdata~\cite{Sinha15:MAG}, and published in the same years, similar to~\cite{Wang16TIST}.
We used all pairs (around 50,000) for \aan, and randomly chose 300,000 pairs for both \aminer and \magdata.

@@

\stitle{Implementation}.
All algorithms were implemented with Microsoft Visual C++.
%Parameters.
For all algorithms, (a) the damping parameter $d$ and the iteration threshold $\epsilon$ were fixed to 0.85 and $10^{-8}$, respectively,
(b) the default splitting years (time) were selected such that the part of data for ranking model accounted for around 75\% of the entire data, which were 2008 on \aan and 2012 on both \aminer and \magdata, and,
(c) for the sake of fairness, aggregating parameters of \futurerank, \hhgrank and \ensemblerank were tuned at the granularity of 0.1 and the best results were reported.
%
Moreover, $\rho$ was set to -0.2 for \futurerank following~\cite{sayyadi09}, and the time decaying factor $\sigma$ and the importance weighting factor $\lambda$ were set to -1 and 0.5  by default for \ensemblerank.

All experiments were conducted on a PC with 2 Intel Xeon E5--2630 2.4GHz CPUs and 64 GB of memory, running 64 bit Windows 7 professional system. The usage of virtual memory was forbidden. %in all of our tests.
When quantity measures were evaluated, the test was repeated over 5 times and the average is reported.

@@

%\etitle{Remarks}.
In our tests we adopted a yearly update policy due the limitation of  available time information. In practice our algorithms may bring more efficiency benefits since the update is usually more frequent, such that the data updates are smaller and the unaffected area is very likely much larger.

@@

When varying $\alpha$ and $\beta$, the \PairAcc of \ensemblerank changes gently, as shown in Fig.~\ref{exp-ab}.
The optimal \PairAcc is obtained within a single region, rather than a complex collection of optimal regions.
%
Moreover, the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, as shown in Fig.~\ref{exp-ab}.
%For instance, consider a square of length 0.3, which covers 8.5\% of the parameter combination space. The fraction of parameters such that the \PairAcc is no worse than 1\% of the corresponding \PairAcc with marker $*$ is (73\%, 94\%) on \aan, (96\%, 87\%) on \aminer and (83\%, 95\%) on \magdata, using (\recom, \fcita), respectively.
%
Further, the optimal parameters on the same set of ground-truth are very similar for (\aan, \aminer and \magdata), indicating that the setting of $\alpha$ and $\beta$ can be easily transferred across different datasets.
To conclude, \ensemblerank is very robust to parameters $\alpha$ and $\beta$, and it is quite flexible for choosing proper values of parameters $\alpha$ and $\beta$.

@@

When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than exploiting exponentially decayed weights directly without introducing the peak time.
The \PairAcc difference of these two algorithms is higher with \recom than with \fcita, since the two algorithms are just using citation information to predict past and future citations with \fcita.
Moreover, algorithm \ensemblerank is consistently better than \drank when $0.5 \le \lambda \le 0.9$.
%, which, with \recom and \fcita, improves the \PairAcc by (2.88\%, 3.91\%, 3.90\%) and (0.55\%, 0.50\%, 0.22\%) on (\aan, \aminer, \magdata) on average, respectively.
The improvement decreases with the decrease of $\lambda$ as the popularity dominates the ranking with small $\lambda$, and in some cases, \drank outperforms \ensemblerank. %as the prestige and popularity orders of article pairs are more diverse for \drank than \ensemblerank.
Overall, with \recom and \fcita, \ensemblerank improves the \PairAcc over \drank by (1.78\%, 3.07\%, 3.20\%) and (0.29\%, 0.48\%, 0.11\%) on (\aan, \aminer, \magdata) on average, respectively.

### 2017-09-30 icde/sec-incAlg.tex

As the popularity of articles is defined as the freshness sum of all their citations, it is convenient to maintain in a dynamic scenario. Consider an updated citation graph $G^{c,+}(V^c\cup\Delta V^c, E^c\cup\Delta E^c)$ of $G^c(V^c, E^c)$, and the updated popularity $Pop_{c}^+(v)$ can be computed as:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
\noindent
where $Pop_c(v)$ (resp. $Pop_c^+(v)$) is the popularity of node $v$ on $G^c$ (resp. $G^{c,+}$), and
 $T_0$ (resp. $T^+_0$) is the current time in $G^c$ (resp. $G^{c,+}$).
%
By Eq.~(\ref{eq-inc-pop}), it is easy to see that it takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time to update the popularity.
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.

>>>>

As the popularity of articles is defined as the sum of the freshness of all their citations, it is convenient to maintain in a dynamic scenario. Consider an updated citation graph $G^{c,+}(V^c\cup\Delta V^c, E^c\cup\Delta E^c)$ of $G^c(V^c, E^c)$, and the updated popularity $Pop_{c}^+(v)$ can be computed as:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
\noindent
where $Pop_c(v)$ (resp. $Pop_c^+(v)$) is the popularity of node $v$ on $G^c$ (resp. $G^{c,+}$), and
 $T_0$ (resp. $T^+_0$) is the current time on $G^c$ (resp. $G^{c,+}$).
%
By Eq.~(\ref{eq-inc-pop}), it is easy to see that it takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time to update the popularity.
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.

### 2017-09-30 icde/sec-model.tex

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
In general, {\em the impact of an article tends to decay with time after the peak time only}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

@@

Based on the above discussion, we propose TWPageRank that evaluates the prestige of nodes (\eg scholarly articles) in a directed graph, such that each node is attached with time information. It differs from PageRank by weighting the influence propagation using the {\em impact weights on edges}, which represent the relative amounts of time-dependent prestige that should be propagated from the edge sources to targets.
%
Formally, the impact weight on a directed edge $(u,v)$, \ie an edge from $u$ to $v$, is defined as:

@@

For scholarly article ranking, $T_u$ is the publication time of article $u$ and $Peak_v$ should be ideally set to the time when article $v$ has the highest impacts. Basically, it could simply be the year when article $v$ obtains the largest number of citations. However, recent work reveals that the volume of scientific publications as well as the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}. We also collect and report the citation statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution. Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of citations at year $t$, respectively. The peak time $Peak_v$ is the time that maximizes $\Psi_v^{(t)}$.
%(\aan, \aminer and \magdata)
% since scholarly data is dynamic and continuously growing
%, and the increased number of references of each article over time
%Recent work observes that the volume of scientific publications doubled every 12 years between 1900 and 2015~\cite{Dong2017KDD}. It is not surprising that the number of references also grows exponentially~\cite{BornmannM15}.

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-twpr}
PR(v)=d\sum_{(u,v)\in E} \frac{w(u,v)PR(u)}{W(u)}+\frac{1-d}{n},
\end{equation}
\end{small}
%
\noindent where $PR(u)$ and $PR(v)$ are the TWPageRank scores of $u$ and $v$, respectively, $E$ is the set of edges, $W(u)=\Sigma_{v} w(u,v)$ is the sum of the impact weights on all edges from $u$, $n$ is the number of nodes and $d$ is a damping parameter in $(0, 1)$. By Eq.~(\ref{eq-twpr}), we can see that prestige is based on the impact weights, not equally distributed.

@@

\stitle{Ranking with importance assembling}. The aforementioned importance is finally assembled to produce the final ranking, as illustrated in Fig.~\ref{fig-rankmodel}. Before assembling, each component is properly scaled such that the average citation importance score, venue importance score and author importance score
are the same.  Let the scaled importance scores of article $v$ be $R_c(v)$, $R_v(v)$, and $R_a(v)$ from the citation, venue and author components, respectively. The final ranking score $R(v)$ of an article $v$ is aggregated as follows:

>>>>

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years   (but not the last year) after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
In general, {\em the impact of an article tends to decay with time after the peak time only}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

@@

Based on the above discussion, we propose TWPageRank that evaluates the prestige of nodes (\eg scholarly articles) in a directed graph, such that each node is attached with time information. It differs from PageRank by weighing the influence propagation using the {\em impact weights on edges}, which represent the relative amounts of time-dependent prestige that should be propagated from the edge sources to targets.
%
Formally, the impact weight on a directed edge $(u,v)$, \ie an edge from $u$ to $v$, is defined as:

@@

For scholarly article ranking, $T_u$ is the publication time of article $u$ and $Peak_v$ should be ideally set to the time when article $v$ has the highest impact. Basically, it could simply be the year when article $v$ obtains the largest number of citations. However, recent work reveals that the volume of scientific publications as well as the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}. We also collect and report the citation statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution. Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of citations at year $t$, respectively. The peak time $Peak_v$ is the time that maximizes $\Psi_v^{(t)}$.
%(\aan, \aminer and \magdata)
% since scholarly data is dynamic and continuously growing
%, and the increased number of references of each article over time
%Recent work observes that the volume of scientific publications doubled every 12 years between 1900 and 2015~\cite{Dong2017KDD}. It is not surprising that the number of references also grows exponentially~\cite{BornmannM15}.

@@

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-twpr}
PR(v)=d\sum_{(u,v)\in E} \frac{w(u,v)PR(u)}{W(u)}+\frac{1-d}{n},
\end{equation}
\end{small}
%
\noindent where $PR(u)$ and $PR(v)$ are the TWPageRank scores of $u$ and $v$, respectively, $E$ is the set of edges, $W(u)=\Sigma_{v} w(u,v)$ is the sum of the impact weights on all edges from $u$, $n$ is the number of nodes and $d$ is a damping parameter in $(0, 1)$. By Eq.~(\ref{eq-twpr}), we can see that prestige is updated based on the impact weights, not equally distributed.

@@

\stitle{Ranking with importance assembling}. The aforementioned importance is finally assembled to produce the final ranking, as illustrated in Fig.~\ref{fig-rankmodel}. Before assembling, each component is properly scaled such that the average importance scores of citations, venues and authors are the same.  Let the scaled importance scores of article $v$ be $R_c(v)$, $R_v(v)$, and $R_a(v)$ from the citation, venue and author components, respectively.

The final ranking score $R(v)$ of an article $v$ is aggregated as follows:

### 2017-09-30 icde/sec-related.tex

Scholarly article ranking has shifted from citation count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{Waltman2014,Jiang12-MRank,Liang16AAAI,Li08TSRanking,Wang13AAAI,WalkerXKM07,sayyadi09,
Wang16TIST,Ng11KDD}.
Based on the information used, these methods are divided into four categories: (a) using the citation information only~\cite{Garfield471,Hirsch15112005,Ng11KDD}, (b) using the citation and temporal information~\cite{Li08TSRanking,WalkerXKM07}, (c) using the citation information and other heterogeneous information, \eg authors and venues of articles~\cite{Jiang12-MRank,Liang16AAAI}, and (d) combining the citation, temporal and other heterogeneous information~\cite{sayyadi09,Wang16TIST,Wang13AAAI}.
Our work belongs to the last category aiming at fully employing information available for scholarly article ranking.
%
%Moreover, recent work has also leveraged external data to improve the ranking quality, \eg using Knowledge Graph Embedding to better understand the meaning of research concepts~\cite{XiongPCWWW17}, and has explored scientific journal ranking \cite{PackalenB17} and scholar ranking \cite{ZhangNBKZX17}. Different from these, our work ranks articles based on scholarly data only.

>>>>

Scholarly article ranking has shifted from citation-count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{Waltman2014,Jiang12-MRank,Liang16AAAI,Li08TSRanking,Wang13AAAI,WalkerXKM07,sayyadi09,
Wang16TIST,Ng11KDD}.
Based on the information used, these methods are divided into four categories: (a) using the citation information only~\cite{Garfield471,Hirsch15112005,Ng11KDD}, (b) using the citation and temporal information~\cite{Li08TSRanking,WalkerXKM07}, (c) using the citation information and other heterogeneous information, \eg authors and venues of articles~\cite{Jiang12-MRank,Liang16AAAI}, and (d) combining the citation, temporal and other heterogeneous information~\cite{sayyadi09,Wang16TIST,Wang13AAAI}.
Our work belongs to the last category aiming at fully employing information available for scholarly article ranking.
%
%Moreover, recent work has also leveraged external data to improve the ranking quality, \eg using Knowledge Graph Embedding to better understand the meaning of research concepts~\cite{XiongPCWWW17}, and has explored scientific journal ranking \cite{PackalenB17} and scholar ranking \cite{ZhangNBKZX17}. Different from these, our work ranks articles based on scholarly data only.
